Deep learning for geophysics

### 2024-06-06 authorship_declaration.tex
Restore signed declarations page

\newpage{}
\noindent{}The contributions of the author have been truthfully stated, and permission from
each author has been sought to include the published material in this thesis.

% \vspace*{20 mm}

\noindent\begin{tabular}{ll}
                                            &                           \\[8ex]
      \makebox[100 mm]{\dotfill}            & \makebox[30 mm]{\dotfill} \\
      Eun-Jung Holden                       & Date                      \\
      Principal and Coordinating Supervisor &                           \\[8ex]
      \makebox[100 mm]{\dotfill}            & \makebox[30 mm]{\dotfill} \\
      Daniel Wedge                          & Date                      \\
      Co-supervisor                         &                           \\[8ex]
      \makebox[100 mm]{\dotfill}            & \makebox[30 mm]{\dotfill} \\
      Tom Horrocks                          & Date                      \\
      Co-supervisor                         &                           \\[8ex]
      \makebox[100 mm]{\dotfill}            & \makebox[30 mm]{\dotfill} \\
      Naveed Akhtar                         & Date                      \\
      Co-supervisor                         &                           \\
\end{tabular}

>>>>

% \newpage{}
% \noindent{}The contributions of the author have been truthfully stated, and permission from
% each author has been sought to include the published material in this thesis.

% % \vspace*{20 mm}

% \noindent\begin{tabular}{ll}
%                                             &                           \\[8ex]
%       \makebox[100 mm]{\dotfill}            & \makebox[30 mm]{\dotfill} \\
%       Eun-Jung Holden                       & Date                      \\
%       Principal and Coordinating Supervisor &                           \\[8ex]
%       \makebox[100 mm]{\dotfill}            & \makebox[30 mm]{\dotfill} \\
%       Daniel Wedge                          & Date                      \\
%       Co-supervisor                         &                           \\[8ex]
%       \makebox[100 mm]{\dotfill}            & \makebox[30 mm]{\dotfill} \\
%       Tom Horrocks                          & Date                      \\
%       Co-supervisor                         &                           \\[8ex]
%       \makebox[100 mm]{\dotfill}            & \makebox[30 mm]{\dotfill} \\
%       Naveed Akhtar                         & Date                      \\
%       Co-supervisor                         &                           \\
% \end{tabular}

### 2024-06-06 manuscript.tex
Make TOC neater
Restore signed declarations page

\newpage{}
\addsec[Declarations]{Thesis Declaration}
I, Luke Thomas Smith, certify that:
\begin{itemize}
    \item{}This thesis has been substantially accomplished during enrolment in this degree.
    \item{}This thesis is my own work and does not contain any material previously published or written by another person, except where due reference has been made in the text or Authorship Declaration.
    \item{}This thesis does not contain material which has been submitted for the award of any other degree or diploma in my name, in any university or other tertiary institution.
    \item{}In the future, no part of this thesis will be used in a submission in my name, for any other degree or diploma in any university or other tertiary institution without the prior approval of The University of Western Australia and where applicable, any partner institution responsible for the joint-award of this degree.
    \item{}This thesis does not violate or infringe any copyright, trademark, patent, or other rights whatsoever of any person.
\end{itemize}

@@

\newpage{}
\input{authorship_declaration}
% Fix incorrect page numbering on the signed form:
% \includepdf[pages=-,templatesize={595.276pt}{841.89pt},nup=1x1,scale=1,clip,trim=5mm 36.5mm 5mm 20mm,fitpaper=true,pagecommand={\pagestyle{plain}}]{authorship_declaration_signed.pdf}

>>>>

\newpage{}
\addsec*[Declarations]{Thesis Declaration}
I, Luke Thomas Smith, certify that:
\begin{itemize}
    \item{}This thesis has been substantially accomplished during enrolment in this degree.
    \item{}This thesis is my own work and does not contain any material previously published or written by another person, except where due reference has been made in the text or Authorship Declaration.
    \item{}This thesis does not contain material which has been submitted for the award of any other degree or diploma in my name, in any university or other tertiary institution.
    \item{}In the future, no part of this thesis will be used in a submission in my name, for any other degree or diploma in any university or other tertiary institution without the prior approval of The University of Western Australia and where applicable, any partner institution responsible for the joint-award of this degree.
    \item{}This thesis does not violate or infringe any copyright, trademark, patent, or other rights whatsoever of any person.
\end{itemize}

@@

\newpage{}
\input{authorship_declaration}
% Fix incorrect page numbering on the signed form:
\includepdf[pages=2,templatesize={595.276pt}{841.89pt},nup=1x1,scale=1,clip,trim=5mm 36.5mm 5mm 20mm,fitpaper=true,pagecommand={\pagestyle{plain}}]{authorship_declaration_signed.pdf}
